Characterizing Signal Loss, Error, and Bias in the 21cm Reionization \\Power Spectrum: A Revised Study of PAPER-64

### 2018-03-23 PAPER.tex
fixed small typos in Appendix

Recalling that $p_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss. This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was original a quadratic estimator is no longer quadratic, but contains higher-order correlations. This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e., quadratic) statistics \citep{LT11}. The result is an improperly normalized---and thus lossy---power spectrum estimate.

>>>>

Recalling that $p_\alpha$ is the \emph{true} power spectrum, one sees that when the covariance in the optimal quadratic estimator is naively replaced by an empirical covariance, the resulting power spectrum estimate is biased low, i.e., there is signal loss. This occurs because of couplings between $\widehat{\C}$ and $\x$, which formally means that what was originally a quadratic estimator is no longer quadratic, but contains higher-order correlations. This violates the assumptions implicit in the derivation of $F_{\alpha \alpha}$ as the normalization factor for converting unnormalized bandpowers $\frac{1}{2} \x^t \C^{-1} \Q^{\alpha} \C^{-1} \x$ into properly normalized power spectrum estimates, where the unnormalized bandpowers are assumed to be two-point (i.e. quadratic) statistics \citep{liu_tegmark2011}. The result is an improperly normalized---and thus lossy---power spectrum estimate.
